---
title: "Lab 4: Data Visualization"
author: "YOUR NAME HERE"
date: ""
format: 
  html:
    embed-resources: true
    code-tools: true
    code-summary: "Code"
draft: false
---

Remember, **follow the instructions below and use R Markdown to create an html document with your code and answers to the following questions.** You may find a template file by clicking "Code" in the top right corner of this page.


```{r}
# LOAD ANY RELEVANT PACKAGES HERE
```

## A. Basic visualizations

For this portion, we'll be using the `palmerpenguins` data. Use the following code to load the data.

```{r}
library(palmerpenguins)
data(penguins)
```

1.  Create and interpret a histogram of `bill_length_mm` using base R code. Be sure to use meaningful axis labels and titles.

2.  Create and interpret a histogram of `bill_length_mm` using ggplot2. Be sure to use meaningful axis labels and titles.

3.  Create and interpret a scatterplot of `bill_length_mm` versus `bill_depth_mm` using base R code. Be sure to use meaningful axis labels and titles.

4. Create and interpret a scatterplot of `bill_length_mm` versus `bill_depth_mm` using ggplot2. Be sure to use meaningful axis labels and titles.

5. Update your `ggplot2` scatterplot of `bill_length_mm` versus `bill_depth_mm` using ggplot2 so that the color of a point represents the corresponding penguin's species. 


## B. Analyzing trends in San Jose rental prices 

For this component, you will be exploring and visualizing data on Craigslist apartment rental postings in the Bay Area. The data are available [here](https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-07-05/rent.csv) from Tidy Tuesday, as prepared by [Dr. Kate Pennington](https://github.com/rfordatascience/tidytuesday/blob/master/data/2022/2022-07-05/readme.md). Note that you can use links within `read_csv()` to read online .csv files. I recommend saving a version of the unprocessed .csv on your machine in a `data` subfolder within your project folder so you will be able to work offline.

6. How many 1 bedroom listings from Santa Clara county are in this dataset?

7. What is the median price for a 1 bedroom listing in Santa Clara county in 2018?

8. Which county has the highest median price for a 1 bedroom listing in 2018?

9. Create two histograms for the prices of 1 bedroom listings in Santa Clara county in 2005 and 2018. Compare and discuss.

10. Create and interpret a line plot with year on the x-axis and median price for a 1 bedroom apartment for Santa Clara county on the y-axis from 2000 to 2018. 

11. Create and interpret a single plot with year on the x-axis and median price for a 1 bedroom apartment on the y-axis, using a separate line for each city in Santa Clara county, for the years 2000 to 2018. 

## C. Open ended data visualization

For this part, choose a dataset that interests you and identify a set of questions that you would like to explore via calculating relevant summary statistics or data visualizations. In particular, you should create three summary tables or visualizations that satisfy the following requirements.

### Instructions

* Identify three research questions of interest that you want to study using this dataset.
* For each of your three research questions, generate a summary statistic, table, or data visualization using your dataset. Discuss and interpret your findings. 
* Each table or visualization should include a caption that fully explains how to understand it (i.e. explain all the components, legends, etc.). A good guideline is that someone who has not read your report should be able to read the caption and fully understand what that table or visualization is showing.
* Each table or visualization must be accompanied by at least one paragraph of text. This text should include an interpretation of your table or visualization as well as what is interesting about it. A strong table or visualization will be accompanied by text explaining what patterns or insights it helps us glean from the data. 
