---
title: "Lab 6"
author: "YOUR NAME HERE"
format: 
  html:
    embed-resources: true
    code-tools: true
    code-summary: "Code"
---

Remember, **follow the instructions below and use R Markdown to create an html document with your code and answers to the following questions.** You may find a template file by clicking "Code" in the top right corner of this page.

## A.. Skewness and Kurtosis

Skewness describes how asymmetrical the distribution of a numerical variable is around its mean. Given observations $x_1,\ldots, x_n$, we can calculate the sample skewness $s$ of a variable using the following formula:

$$s = \frac{\frac{1}{n}\sum\limits_{i=1}^n(x_i-\overline{x})^3}{\left[\frac{1}{n}\sum\limits_{i=1}^n(x_i-\overline{x})^2\right]^{3/2}}$$
Kurtosis is a measure of the "tailedness" of the distribution of a numerical variable is around its mean. Higher values of kurtosis indicate more extreme outliers. Given observations $x_1,\ldots, x_n$, we can calculate the sample kurtosis $k$ of a variable using the following formula:

$$k = \frac{\frac{1}{n}\sum\limits_{i=1}^n(x_i-\overline{x})^4}{\left[\frac{1}{n}\sum\limits_{i=1}^n(x_i-\overline{x})^2\right]^{2}}-3$$

1. Write a function `skewness()` that takes as input a numeric vector `x` and returns the sample skewness. There are functions in R that compute skewness, but you cannot use any of them--write your own implementation. You may remove all `NA` values by default. Use your function to compute the sample skewness of the `arr_delay` variable in the `flights` dataset contained in the `nycflights13` package.

2. Write a function `kurtosis()` that takes as input a numeric vector `x` and returns the sample skewness. There are functions in R that compute kurtosis, but you cannot use any of them--write your own implementation. You may remove all `NA` values by default. Use your function to compute the sample kurtosis of the `arr_delay` variable in the `flights` dataset contained in the `nycflights13` package.

3. Write a function `get_column_skewness()` that takes as input a data frame and calculates the skewness of each **numeric** variable. The output should be a data frame with two variables: `variable` containing the name of the variable and `skewness` containing the skewness. Your output data frame should only include the numeric variables. You may remove all `NA` values by default. Demonstrate your function on the `penguins` dataset.

## B. Finding an error

Suppose you have two teams of runners participating in a 5k. We wish to write a function that takes as input two vectors representing the times of the runners in each team and returns a list of two vectors representing the ranks of each team's runners.

For example, if the first team's times are `c(16.8, 21.2, 19.1)` and the second team's times are `c(17.2, 18.1, 20.0)`, the function should return `c(1, 6, 4)` for the first team and `c(2, 3, 5)` for the second team. 

Below is a draft version of the function `get_runner_ranks()`. However, there is an error somewhere. Use any method we discussed in class to identify the error.

```{r, error = T, echo = T, eval = T}
get_runner_ranks <- function(x, y) {
  # combine all runner times
  combined_times <- c(x, y) 
  
  # sort all runner times from fastest to slowest
  sort(combined_times, decreasing = T)
  
  # create ranks vectors
  ranks_x <- numeric(length(x))
  ranks_y <- numeric(length(y))
  
  for (i in seq_along(ranks_x)) {
    # look up rank of time i in x in combined_times
    ranks_x[i] <- match(x[i], combined_times)
  }
  
  for (i in seq_along(ranks_y)) {
    # look up rank of time i in y in combined_times
    ranks_y[i] <- match(y[i], combined_times)
  }
  
  # return a list of first team and second team ranks
  return(list(x = ranks_x, y = ranks_y))
}
```

4. Explain in your own words what the error was.

5. Below, write a corrected version of `get_runner_ranks()` and compute `get_runner_ranks(c(16.8, 21.2, 19.1), c(17.2, 18.1, 20.0))`.

```{r, error = T, echo = T, eval = T}
get_runner_ranks <- function(x, y) {
  # YOUR CODE HERE
}
```

## C. Enumerating possibilities

6. Consider the following problem. If I randomly arrange $2$ Coke cans and $2$ Pepsi cans in a row, how many different **distinguishable** orderings are there? In this case, there are $4!/(2!\times 2!)=6$ orderings: CCPP, CPCP, CPPC, PPCC, PCPC, PCCP. Write a function `get_distinguishable_orderings()` that takes two inputs, $m$ and $n$, and returns a vector containing all distinguishable orderings of $m$ Coke cans and $n$ Pepsi cans. In other words, `get_distinguishable_orderings(2, 2)` should return the vector `"CCPP" "CPCP" "CPPC" "PPCC" "PCPC" "PCCP"` (or a reordered version of this vector).

7. Use your function to create a vector of all distinguishable orderings of $3$ Coke cans and $3$ Pepsi cans. Print this vector.
